Demo: Counterpoint by Construction

### 2019-06-25 doc/farm/farm-abstract.tex
tweaks

The goal of Music Tools is to provide a core collection of types and functions
that can be used to easily build applications to analyze and synthesize music.
It is intended to evolved into a dependently-typed replacement for Euterpea
\citep{hudak2018haskell} and borrows many ideas from that library.
It is currently restricted to the chromatic scale for simplicity, and like
Euterpea is designed to work well with MIDI.

The fundamental type for melody is \texttt{Pitch} which is just a natural number with $0$
representing the lowest expressible pitch (it is intended to correspond to MIDI note 0, but
the interpretation can change depending upon the application). One can also
express pitch as a pair of an octave and relative pitch within the ocatve, which is
more convenient for some applications, and convert between this representation and
absolute pitch. One can then prove that converting back and forth is the identity function.

@@

Music in turn can be converted to MIDI and and played on synthesizers. Existing Haskell
MIDI libraries are called via Agda's Haskell FFI. Details can be found in the github
repository.

@@

Music is a rich yet circumscribed domain in which
issues of equivalence \citep{tabareau2017equivalences}
and ornamentation \citep{dagand2017essence} naturally arise.
For example a
musical score can be interpreted either horizontally (counterpoint) or
vertically (harmony) and it is important to be able to seamlessly
convert between these representations. Similarly one may wish to treat
pitch or rhythm separately as well as combine them, which is a natural
application of ornamentation. We plan to examine the extent to which this
research can be put to use in a practical domain.

For counterpoint specifically, we plan represent higher species counterpoint
and also to explore automatic generation of species counterpoint,
contrasting the music created to recent work on generating
natural-sounding counterpoint by machine learning
\citep{CounterpointByConvolution}, which does not provide correctness
guarantees.

>>>>

The goal of Music Tools is to provide a core collection of types and functions
that can be used to easily build applications to analyze and synthesize music.
It is intended to evolve into a dependently-typed replacement for Euterpea
\citep{hudak2018haskell} and borrows many ideas from that library.
It is currently restricted to the chromatic scale for simplicity, and like
Euterpea is designed to work well with MIDI.

The fundamental type for melody is \texttt{Pitch}, which is just a natural number with $0$
representing the lowest expressible pitch (it is intended to correspond to MIDI note 0, but
the interpretation can change depending upon the application). One can also
express pitch as a pair of an octave and relative pitch within the octave, which is
more convenient for some applications, and convert between this representation and
absolute pitch. One can then prove that converting back and forth is the identity function.

@@

To play music on synthesizers, one can convert it to MIDI by calling 
Haskell MIDI libraries via Agda's Haskell FFI. 
Details can be found in the github repository.

@@

Music is a rich yet circumscribed domain in which
issues of equivalence \citep{tabareau2017equivalences}
and ornamentation \citep{dagand2017essence} naturally arise.
For example, a
musical score can be interpreted either horizontally (counterpoint) or
vertically (harmony), and it is important to be able to seamlessly
convert between these representations. Similarly, one may wish to treat
pitch or rhythm separately as well as combine them, which is a natural
application of ornamentation. We plan to examine the extent to which this
research can be put to use in a practical domain.

For counterpoint specifically, we plan to represent higher species 
counterpoint by extending the rules, 
and to explore automatic generation of species counterpoint.
It would be interesting to compare our correct-by-construction counterpoint
and one created by machine learning \citep{CounterpointByConvolution}, 
which does not have correctness guarantees.
